---
title: "HouseHunters"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(DT)
dat <- read.csv("value_house.csv", stringsAsFactors = FALSE)
hunter_dat <- dat %>%
  drop_na(list_price)
```

Map
=======================================================================

Row {data-height=675}
-----------------------------------------------------------------------

### Map of Housing Options
```{r, include=FALSE}
getColor <- function(dat) {
  color_vec <- lapply(dat$value_category, function(value_cat) {
    if (value_cat == "high") {
      "blue"
    } else if (value_cat == "med") {
      "green"
    } else {
      "red"
    }
  })
  unlist(color_vec)
}
```

```{r high price, include=FALSE}
# creating high price data, labels, and icons
high_price_dat <- hunter_dat %>%
  filter(price_category == "high")
high_price_labels <- sprintf("<strong>%s</strong><br/>List Price: $%s",
                  high_price_dat$address,
                  scales::comma(high_price_dat$list_price)) %>%
  lapply(htmltools::HTML)
high_price_icons <- awesomeIcons(
  iconColor = 'black',
  markerColor = getColor(high_price_dat)
)
```

```{r med price, include=FALSE}
# creating medium price data, labels, and icons
med_price_dat <- hunter_dat %>%
  filter(price_category == "med")
med_price_labels <- sprintf("<strong>%s</strong><br/>List Price: $%s",
                  med_price_dat$address,
                  scales::comma(med_price_dat$list_price)) %>%
  lapply(htmltools::HTML)
med_price_icons <- awesomeIcons(
  iconColor = 'black',
  markerColor = getColor(med_price_dat)
)
```

```{r low price, include=FALSE}
# creating low price data, labels, and icons
low_price_dat <- hunter_dat %>%
  filter(price_category == "low")
low_price_labels <- sprintf("<strong>%s</strong><br/>List Price: $%s",
                  low_price_dat$address,
                  scales::comma(low_price_dat$list_price)) %>%
  lapply(htmltools::HTML)
low_price_icons <- awesomeIcons(
  iconColor = 'black',
  markerColor = getColor(low_price_dat)
)
```

```{r}
leaflet() %>%
  setView(lng = mean(hunter_dat$longitude),
          lat = mean(hunter_dat$latitude) + 0.075,
          zoom = 10) %>%
  addTiles() %>%
  addAwesomeMarkers(data = high_price_dat,
                    lng = ~longitude,
                    lat = ~latitude,
                    icon = high_price_icons,
                    popup = high_price_labels,
                    group = "High") %>%
  addAwesomeMarkers(data = med_price_dat,
                    lng = ~longitude,
                    lat = ~latitude,
                    icon = med_price_icons,
                    popup = med_price_labels,
                    group = "Medium") %>%
  addAwesomeMarkers(data = low_price_dat,
                    lng = ~longitude,
                    lat = ~latitude,
                    icon = low_price_icons,
                    popup = low_price_labels,
                    group = "Low") %>%
  addLayersControl(
    overlayGroups = c("High", "Medium", "Low"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function() {
            $('.leaflet-control-layers-overlays').prepend('<label style=\"text-align:center\">Price Category</label>');
        }    
  ") %>%
  addLegend(position = "bottomright",
            title = "Value Category",
            colors = c("Blue", "Green", "Red"),
            labels = c("High", "Medium", "Low"))
```

Analysis
=======================================================================

Row {data-height=250}
-----------------------------------------------------------------------

### Data Table

```{r}
hunter_DT <- hunter_dat %>%
  select(address, bed, bathroom, sq_footage, hunter_mins, stewart_mins,
        list_price, value) %>%
  mutate(list_price = paste0("$", scales::comma(list_price)),
         hunter_mins = paste0(hunter_mins, " minutes"),
         stewart_mins = paste0(stewart_mins, " minutes"),
         value = round(value, digits = 5)) %>%
  dplyr::rename("Address" = address,
                "List Price" = list_price,
                "Bedrooms" = bed,
                "Bathrooms" = bathroom,
                "Square Footage" = sq_footage,
                "Time to Hunter" = hunter_mins,
                "Time to Stewart" = stewart_mins,
                "List Price" = list_price,
                "Value Score" = value)
datatable(hunter_DT,
          height = 600,
          rownames = FALSE)
```

Row {data-height=650 .tabset}
-----------------------------------------------------------------------

### Square Footage vs. Value

```{r, fig.width=30, fig.height=12}
hunter_dat %>%
  mutate(price_category = factor(price_category, levels = c("low", "med", "high"))) %>%
  ggplot(aes(x = sq_footage,
             y = value,
             color = price_category,
             size = 5)) +
  geom_point() +
  theme_bw(base_size = 28) +
  xlab("Square Feet") +
  labs(color = "Price Category") +
  guides(size = FALSE)
```

### Time to Hunter vs. Value

```{r, fig.width=30, fig.height=12}
hunter_dat %>%
  mutate(price_category = factor(price_category, levels = c("low", "med", "high"))) %>%
  ggplot(aes(x = hunter_mins,
             y = value,
             color = price_category,
             size = 5)) +
  geom_point() +
  theme_bw(base_size = 28) +
  xlab("Time to Hunter (minutes)") +
  labs(color = "Price Category") +
  guides(size = FALSE)
```

### Time to Stewart vs. Value

```{r, fig.width=30, fig.height=12}
hunter_dat %>%
  mutate(price_category = factor(price_category, levels = c("low", "med", "high"))) %>%
  ggplot(aes(x = stewart_mins,
             y = value,
             color = price_category,
             size = 5)) +
  geom_point() +
  theme_bw(base_size = 28) +
  xlab("Time to Stewart (minutes)") +
  labs(color = "Price Category") +
  guides(size = FALSE)
```

### Bedroom Stats

```{r, fig.width=30, fig.height=12}
bed_value <- hunter_dat %>%
  mutate(value_category = factor(value_category,
                                 levels = c("low","med","high"))) %>%
  group_by(bed, value_category) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = bed, y = n, fill = value_category)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw(base_size = 28) +
  scale_x_discrete(name = "Number of Bedrooms",
                   limits = c("1","2","3","4","5","6","7","8","9")) +
  ylab("Count") +
  labs(fill = "Value Category")

bed_price <- hunter_dat %>%
  mutate(price_category = factor(price_category,
                                 levels = c("low","med","high"))) %>%
  group_by(bed, price_category) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = bed, y = n, fill = price_category)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw(base_size = 28) +
  scale_x_discrete(name = "Number of Bedrooms",
                   limits = c("1","2","3","4","5","6","7","8","9")) +
  ylab("Count") +
  labs(fill = "Price Category")

ggpubr::ggarrange(bed_value, bed_price, ncol = 1, nrow = 2)
```

### Bathroom Stats

```{r, fig.width=30, fig.height=12}
bath_value <- hunter_dat %>%
  mutate(value_category = factor(value_category,
                                 levels = c("low","med","high"))) %>%
  group_by(bathroom, value_category) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = bathroom, y = n, fill = value_category)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw(base_size = 28) +
  scale_x_discrete(name = "Number of Bathrooms",
                   limits = c("1","2","3","4","5")) +
  ylab("Count") +
  labs(fill = "Value Category")

bath_price <- hunter_dat %>%
  mutate(price_category = factor(price_category,
                                 levels = c("low","med","high"))) %>%
  group_by(bathroom, price_category) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = bathroom, y = n, fill = price_category)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw(base_size = 28) +
  scale_x_discrete(name = "Number of Bathrooms",
                   limits = c("1","2","3","4","5")) +
  ylab("Count") +
  labs(fill = "Price Category")

ggpubr::ggarrange(bath_value, bath_price, ncol = 1, nrow = 2)
```

Recommendations
=======================================================================

Row {data-height=575}
-----------------------------------------------------------------------

### Cost vs. Value Plot

```{r, fig.width=32, fig.height=11}
good_opts <- c()
for (i in 1:nrow(hunter_dat)) {
  test_val <- hunter_dat[i, "value"]
  test_price <- hunter_dat[i, "list_price"]
  test_X <- hunter_dat[i, "X"]
  better_opts <- hunter_dat %>%
    filter(value >= test_val, list_price <= test_price)
  if (nrow(better_opts) <= 1) {
    good_opts <- c(good_opts, test_X)
  }
}
recs <- hunter_dat %>%
  filter(X %in% good_opts) %>%
  select(X, address, list_price, value)

X5 <- hunter_dat %>%
  filter(X == 5) %>%
  select(X, address, list_price, value)

X42 <- hunter_dat %>%
  filter(X == 42) %>%
  select(X, address, list_price, value)
 
X43 <- hunter_dat %>%
  filter(X == 43) %>%
  select(X, address, list_price, value)

X57 <- hunter_dat %>%
  filter(X == 57) %>%
  select(X, address, list_price, value)

X79 <- hunter_dat %>%
  filter(X == 79) %>%
  select(X, address, list_price, value)

X112 <- hunter_dat %>%
  filter(X == 112) %>%
  select(X, address, list_price, value)

X158 <- hunter_dat %>%
  filter(X == 158) %>%
  select(X, address, list_price, value)

X184 <- hunter_dat %>%
  filter(X == 184) %>%
  select(X, address, list_price, value)

hunter_dat %>%
  ggplot(aes(x = list_price, y = value, size = 5)) +
  geom_point() +
  theme_bw(base_size = 32) +
  guides(size = FALSE, color = FALSE) +
  geom_point(data = recs,
             aes(x = list_price,
                 y = value,
                 size = 5,
                 color = "red")) +
  geom_vline(xintercept = 198100, size = 1, linetype = "dashed") +
  geom_text(data = X5,
            aes(x = list_price, y = value, label = address),
            nudge_x = -19000,
            size = 7) +
  geom_text(data = X42,
            aes(x = list_price, y = value, label = address),
            nudge_x = -20000,
            size = 7) +
  geom_text(data = X43,
            aes(x = list_price, y = value, label = address),
            nudge_x = 10000,
            nudge_y = -0.06,
            size = 7) +
  geom_text(data = X57,
            aes(x = list_price, y = value, label = address),
            nudge_x = -17500,
            nudge_y = 0.005,
            size = 7) +
  geom_text(data = X79,
            aes(x = list_price, y = value, label = address),
            nudge_x = -18500,
            size = 7) +
  geom_text(data = X112,
            aes(x = list_price, y = value, label = address),
            nudge_x = -19750,
            size = 7) +
  geom_text(data = X158,
            aes(x = list_price, y = value, label = address),
            nudge_x = -20000,
            size = 7) +
  geom_text(data = X184,
            aes(x = list_price, y = value, label = address),
            nudge_x = -19500,
            size = 7) +
  annotate("segment", x = 50000, xend = 46100, y = 0.31, yend = 0.348,
           colour = "black", size = 1, alpha = 0.6, arrow = arrow()) +
  ylab("Value") +
  xlab("List Price")
```

Row {data-height=75}
-----------------------------------------------------------------------

### Discussion

This graph shows the cost versus value analysis that produces the recommended housing solutions. Anything to the right of the dashed line indicates a sub-optimal candidate, as they have a lower value for a higher price than other options available. The highlighted houses are all pareto-optimal, meaning that one may have a higher than another, but it will also have a higher cost. For each of these recommendations, there is no other house available that has a higher value for a lower price.